\textls[-0]{\thetitle}

### 2023-03-04 metatheory-condensed.tex
resolve a comment

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type $\TyId{\cDot}{\cDot}$, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
A constructor is given by a pair of types
$\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$ (rule \ruleref{wsig/add}):
given two arguments $\goodTerm{\Gm}{t_1}{A}$ and
$\goodTerm{\Gm,\sub{B}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{T}$,
we can constructs a term $\Wsup{\wsig}{t_1}{t_2}$ of type~$T$ (rule \ruleref{tm/wsup}). \rB{for readability please add text between "T," and "Wsup"}\EDJreply{changed, please review}
As the rules suggest, our formulation additionally supports
\emph{W-type signatures}.
A well formed W-type signature \goodWSig{\Gm}{\wsig}{n} is
composed of $n$ pairs of types, each of which represents a constructor
(rules \ruleref{wsig/empty} and \ruleref{wsig/add}),
with $\wsigproj{i}{1}{\wsig}$ and $\wsigproj{i}{2}{\wsig}$ giving the
$i$-th pair in~$\wsig$, and $\wcode{\wsig}$ giving the code of the W-type (\ruleref{tm/w}).

% Add example for representing tm here

>>>>

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type $\TyId{\cDot}{\cDot}$, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
In the literature,
a W-type is given by a pair of types $\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$,
but our formulation of W-types additionally
allows a W-type signature \goodWSig{\Gm}{\wsig}{n} to
specify $n$ pairs of types (\ruleref{wsig/empty} and \ruleref{wsig/add}).
Each pair models a constructor in an inductive type,
with $\goodType{\Gm}{\wsigproj{i}{1}{\wsig}}{}$
and $\goodType{\Gm,\wsigproj{i}{1}{\wsig}}{\wsigproj{i}{2}{\wsig}}{}$
identifying the $i$-th constructor, and $\wcode{\wsig}$ giving the code of the
W-type (\ruleref{tm/w}).
%
Rule~\ruleref{tm/wsup} states that 
given two arguments $\goodTerm{\Gm}{t_1}{\wsigproj{i}{1}{\wsig}}$ and
$\goodTerm{\Gm,\sub{\wsigproj{i}{2}{\wsig}}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{\El{\wcode{\wsig}}}$,
we can construct a term $\Wsup{\wsig}{t_1}{t_2}$ of the W-type.
